A survey of HTTP caching options on the open Web

### 2015-01-13 sanity/paper1.tex
hardall fig
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@975 43ef1190-90fd-4dd7-a769-d0121f02b80e

Caching may also be prohibited by setting a non-positive freshness
lifetime. Common practice is to set the \httph{Expires} header to a
date far back in time, which has also been done in large parts of the
present dataset. For the following, we have set any non-positive
lifetime to 0, as that is semantically equivalent. With that, we
obtain the summary statistics in Table~\ref{tab:summaryhard}. In
figure\todo{add figure}, we have included a histogram with the counts
of the resources that had 0 lifetime, and then boxes of varying length.

@@

In Figure\todo{figure with over freshness}, there is a barplot where
the freshness lifetime is grouped in bins, where the first bin are the
cases where caching is explicitly prohibited. The next bins are for
lifetimes, where the values are grouped if they are on the order of
seconds, minutes, hours, etc, i.e. the second bin counts the lifetimes
in the interval [1,59] seconds, etc. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days.

>>>>

Caching may also be prohibited by setting a non-positive freshness
lifetime. Common practice is to set the \httph{Expires} header to a
date far back in time, which has also been done in large parts of the
present dataset. For the following, we have set any non-positive
lifetime to 0, as that is semantically equivalent. With that, we
obtain the summary statistics in Table~\ref{tab:summaryhard}.

@@

In Figure~\ref{fig:hardall}, there is a barplot where
the freshness lifetime is grouped in bins. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days.

\begin{figure}[ht!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardall.pdf}}
  \caption{Barplot of all standard-compliant freshness lifetimes
    found. The first bin are the cases where caching is explicitly
    prohibited. The next bins are for lifetimes, where the values are
    grouped if they are on the order of seconds, minutes, hours, etc,
    i.e. the second bin counts the lifetimes in the interval [1,59]
    seconds, etc.}
  \label{fig:hardall}
\end{figure}
